Artin Group Presentations Arising from Cluster Algebras

### 2014-09-25 Paper.tex
Aaron's Suggestion

In the process of writing this paper, we became aware of related results obtained independently by Grant and Marsh in \cite{GM14} and Qiu in \cite{Q14}. Using different approaches, the two papers found relations for the Artin group in the simply-laced cases. However, their relations differ from the ones used in our paper, and our approach to the problem is more combinatorial than the more topological approaches found in \cite{Q14} and \cite{GM14}.

>>>>

In the process of writing this paper, we became aware of related results obtained independently by Grant and Marsh in \cite{GM14} and Qiu in \cite{Q14}. Using different approaches, the two papers found relations for the Artin group in simply-laced diagrams. However, their relations differ from the ones used in our paper, and we show that our results hold for all diagrams of finite type. Furthermore, our approach to the problem is more combinatorial than the topological approaches found in \cite{Q14} and \cite{GM14}.
